### 2020-04-28 Paper/paper.tex
fixed undefined reference problem

The images and scores were read in using a technique similar to the MNIST problem presented in OLA 6. The main difference being that the grab\_image function was modified to read in our images as greyscale rather than full RGB and at a reduced resoultion of 100x100. We then shuffled the images, taking care to manipulate them in such a way that the scores would retain the same index as their respective images. This shuffling ensured that models of similar scores would be randomly distributed, preventing the model from learning soley on one quality of model at a time.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6. In this net, there are two 2D convolution layers that feed into a pooling layerThe main changes made were to kernel size and the final dense layer. There are two 2D convolution layers use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is the passed into a flattening layer and a single dense layer, still with a ReLu activation function, before passing though a final dropout layer and into the final dense layer. The main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.

>>>>

The images and scores were read in using a technique similar to the MNIST problem presented in OLA 6 \cite{phillips}. The main difference being that the grab\_image function was modified to read in our images as greyscale rather than full RGB and at a reduced resoultion of 100x100. We then shuffled the images, taking care to manipulate them in such a way that the scores would retain the same index as their respective images. This shuffling ensured that models of similar scores would be randomly distributed, preventing the model from learning soley on one quality of model at a time.

@@

In our second net, we attempted to utilize the superior image recognition characteristics of a convolutional neural net. As a base, we used the convolutional neural net used on the cat problem in OLA 6 \cite{phillips}. In this net, there are two 2D convolution layers that feed into a pooling layerThe main changes made were to kernel size and the final dense layer. There are two 2D convolution layers use a standard ReLu activation function, which are then followed by pooling and dropout layer. It is the passed into a flattening layer and a single dense layer, still with a ReLu activation function, before passing though a final dropout layer and into the final dense layer. The main changes we made to this architecture from OLA 6 were in terms of kernel size, unit size of the dense and convolution layers, and the setup of the final dense layer.
